Fitness Adventure: an interactive floor game to maintain body fitness

### 2015-01-28 paper.tex
rewrite walkthrough completely .. now almost fills entire page and is much easier to read

\section{Walkthrough}

  % test section
  \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_4.jpg}
    \includegraphics[width=0.32\linewidth]{Image_5.jpg}
    \includegraphics[width=0.32\linewidth]{Image_1.jpg}
    \caption{(left) Enter the floor to start the game. (middle) Step on the spot to move through the world. (right) Jump over fallen trees.}
  \end{figure}

  \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_7.jpg}
    \includegraphics[width=0.32\linewidth]{Image_2.jpg}
    \includegraphics[width=0.32\linewidth]{Image_8.jpg}
    \caption{(left) Reach the sea. (middle) Hold on ice floes to get over. (right) Ice floes will sink, so always switch to a stable one.}
  \end{figure}

  \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_6.jpg}
    \includegraphics[width=0.32\linewidth]{Image_6.jpg}
    \includegraphics[width=0.32\linewidth]{Image_6.jpg}
    \caption{Penalty: (left) Hitting a tree brings 10s time penalty. (middle) Illustration from the side. (right) Touching the water does as well.}
  \end{figure}

  \begin{figure}[!htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_9.jpg}
    \includegraphics[width=0.32\linewidth]{Image_3.jpg}
    \includegraphics[width=0.32\linewidth]{Image_10.jpg}
    \caption{(left) Reach a broken bridge. (middle) Get the wooden planks. (right) Build up the bridge to cross the water. (Remember penalty)}
  \end{figure}
  % end test section

  In this scenario the student Andy trains his body by running in place, jumping a lot, staying in push-ups position and alternating running and touching the floor.

  \begin{figure}[!htb]
  \minipage{0.5\textwidth}
    \includegraphics[width=\linewidth]{Image_11.jpg}
  \endminipage\hfill
    \caption{Task Overview. (1) Andy runs in place and jumps over trees. (2) Water appeared  with some ice floes on it and Andy has to stay on these, but they melt. (3) Andy has to build a bridge to cross the water.}\label{fig:awesome_image3}
  \end{figure}

  The conrete beginning of the game (Figure 3 (1)) includes more thoughts. We focus on it in detail.

  \begin{figure}[!htb]
  \minipage{0.5\textwidth}
    \includegraphics[width=\linewidth]{Image_12.jpg}
  \endminipage\hfill
    \caption{(1) Andy is entering the floor and immediatly instructed to start running. The floor will begin to move under his feet. (2) When trees appear on the way, Andy has to jump over them. (3) When Andy unintentionally lands on a tree, he is punished with extra time (time is counting forwarsds and stopped, when one run is finished).}\label{fig:awesome_image3}
  \end{figure}

  \begin{figure}[!htb]
  \minipage{0.5\textwidth}
    \includegraphics[width=\linewidth]{Image_13.jpg}
  \endminipage\hfill
    \caption{(1) Andy runs over a beach and approaches water with ice floes on it. He is instructed to jump on them. (2) After jumping on the icefloes, he put his hand onto the other ice floes. (3) When an ice floe melts, others appear, Andy has to put the hand on.}\label{fig:awesome_image3}
  \end{figure}

  After a the ice floe game, the run proceeds as already shown in figure 3.

  \begin{figure}[!htb]
  \minipage{0.5\textwidth}
    \includegraphics[width=\linewidth]{Image_14.jpg}
  \endminipage\hfill
    \caption{(1) Andy runs over a beach with wood planks and is instructed to build a bridge to cross the water. (2) Andy touches the floor with his hands on the woodplanks to collect one. (3) He touches the water to build a part of a bridge. (4) Andy did alternating (2) and (3), finished the bridge and proceeds his run.}\label{fig:awesome_image3}
  \end{figure}

@@

  When designing applications for interactive floors, user studies and exploration with prototypes becomes extremely important since there are no patterns and the problem domain is yet unexplored. During the process, our evaluation of the users' needs changed radically. When asking users what they wanted they looked at existing solutions and tried to map them to the floor. If we followed those, we would have ended up with a fitness mat and a video player. This, however, is already an existing solution for people without any sport equipment. We collected important aspects from users: the need for motivation and limited free time. First we mapped them to possible exercises on the floor and later came to the conclusion, that games are the most interactive solution motivating users with fun when doing workouts. The ability to challenge your highscore, pushes your goals and visualize your progress. 
  Developing an interactive protoype for a floor requires a lot amount of work. Paper prototyping turned out to be a powerful tool in order to find flaws in our designs as users were able to imagine the system.
  Even when users want to do fitness activity with our application, they look for the simplest solution to solve a game. Therefore we need to design fitness games that forces users to do certain activity instead of giving them the freedom on how they want to solve a task.

>>>>

\section{Walk-through}

  \subsection{Old Forest: the first territory in the game} % (fold)

    \begin{figure}[htb]
      \centering
      \includegraphics[width=0.32\linewidth]{Image_4.jpg}
      \includegraphics[width=0.32\linewidth]{Image_5.jpg}
      \includegraphics[width=0.32\linewidth]{Image_1.jpg}
      \caption{(left) Enter the floor to start the game. (middle) Step on the spot to move through the world. (right) Jump over fallen trees.}
      \label{fig:start}
    \end{figure}

    In this scenario, the student Andy wants to do his regular activity and get exhausted. The specific task is about to raise his heart rate over 180. Therefore, Andy enters the floor and it tells him to start running (see figure \ref{fig:start} on the left). Andy now steps on the spot and the ground under his feet moves along (figure \ref{fig:start}, in the middle). Whenever he meets a fallen tree, he has to jump over it (figure \ref{fig:start}, on the right). This does not need any explanation, since nobody can walk through a tree. If he does this anyway, he will receive a time penalty of 10 seconds (figure \ref{fig:penalty}, on the left and in the middle).

  \subsection{Arctic Sea: the second territory in the game} % (fold)

    \begin{figure}[htb]
      \centering
      \includegraphics[width=0.32\linewidth]{Image_7.jpg}
      \includegraphics[width=0.32\linewidth]{Image_2.jpg}
      \includegraphics[width=0.32\linewidth]{Image_8.jpg}
      \caption{(left) Reach the sea. (middle) Hold on ice floes to get over. (right) Ice floes will sink, so always switch to a stable one.}
      \label{fig:ice_floe}
    \end{figure}

    After running for a while, Andy will reach the sea. He can obviously not cross it (figure \ref{fig:ice_floe}, on the left). He notices ice floes appearing. He can drift over the water by holding himself on those ice floes (figure \ref{fig:ice_floe}, in the middle). The ice floes sink and melt because of the weight and the warm hands. They begin to get smaller and smaller. Andy has to move from ice floe to ice floe in his position. He does not want to fall into the cold water (figure \ref{fig:ice_floe}, on the right). If he does anyway, he will receive a time penalty of 10 seconds (see again figure \ref{fig:penalty}, the right image).

  \begin{figure}[htb]
    \centering
    \includegraphics[width=0.32\linewidth]{Image_6.jpg}
    \includegraphics[width=0.32\linewidth]{Image_6.jpg}
    \includegraphics[width=0.32\linewidth]{Image_6.jpg}
    \caption{Penalty: (left) Hitting a tree brings 10s time penalty. (middle) Illustration from the side. (right) Touching the water does as well.}
    \label{fig:penalty}
  \end{figure}

  \subsection{Workout World: repeating territories} % (fold)

    When Andy finally arrives at a beach again, he can run further. Depending on the world, he will run through the forest (described in subsection \emph{Old Forest}) and drift over the sea (described in subsection \emph{Arctic Sea}) some more times. This is how the world looks like. There are some areas with different kinds of activities that create a workout together. The same applies to the third territory, the broken bridge.

  \subsection{Broken Bridge: the third territory in the game} % (fold)

    \begin{figure}[htb]
      \centering
      \includegraphics[width=0.32\linewidth]{Image_9.jpg}
      \includegraphics[width=0.32\linewidth]{Image_3.jpg}
      \includegraphics[width=0.32\linewidth]{Image_10.jpg}
      \caption{(left) Reach a broken bridge. (middle) Get the wooden planks. (right) Build up the bridge to cross the water. (Remember penalty)}
      \label{fig:bridge}
    \end{figure}

    Andy now arrives at a river. He can see a bridge, but it is broken. He looks around and finds wooden planks. He now repairs the bridge with the wooden planks by alternately touching the wooden planks and the broken bridge. Therefore he has to repeatedly run between the planks and the bridge. This includes accelerating, stopping and bending down. Once the bridge is repaired, Andy can pass the river and continue his adventure.

  \section{Workout Result: what the user has achieved} % (fold)
  \label{sec:section_name}

    \begin{figure}[htb]
      \centering
      \includegraphics[width=0.32\linewidth]{Image_6.jpg}
      \caption{Final screen; shows the time the user needed to run through the world and the heart rate, if the hardware is available. The user is also congratulated, because he finished the workout.}
      \label{fig:end}
    \end{figure}

    When Andy has run through the world, he will see the final screen. It contains the needed time and his heart rate, as well as a congratulation. The next time, he can try to beat his record. This would require him to step and repair the bridge much faster.

@@

  When designing applications for interactive floors, user studies and exploration with prototypes becomes extremely important since there are no patterns and the problem domain is yet unexplored. During the process, our evaluation of the users' needs changed radically. When asking users what they wanted they looked at existing solutions and tried to map them to the floor. If we followed those, we would have ended up with a fitness mat and a video player. This, however, is already an existing solution for people without any sport equipment. We collected important aspects from users: the need for motivation and limited free time. First we mapped them to possible exercises on the floor and later came to the conclusion, that games are the most interactive solution motivating users with fun when doing workouts. The ability to challenge your highscore, pushes your goals and visualize your progress.

  Developing an interactive protoype for a floor requires a lot amount of work. Paper prototyping turned out to be a powerful tool in order to find flaws in our designs as users were able to imagine the system.

  Even when users want to do fitness activity with our application, they look for the simplest solution to solve a game. Therefore we need to design fitness games that forces users to do certain activity instead of giving them the freedom on how they want to solve a task.

  In the future, the game could also contain a map editor. This would satisfy the users need to configure their workout. In addition, it would make the game more interesting and diversified. There should also be some more territories containing new sport exercises. The users could have to jump a lot, or maybe lift another person.
